\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \textheight=12in
    \pagestyle{empty}
    \raggedright
    \usepackage{fontawesome}
    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=black,
}

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
    % END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}

\vspace*{-10mm}

%==== Profile ====%
%\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Drupad Kumar Singh}}\\
	\href{https://www.linkedin.com/in/drupad-singh-14337712b/}{\faLinkedin}
	$\cdot$
	\href{https://github.com/orton009}{\faGithub}
	$\cdot$
	\href{mailto:drupad.k.singh98@gmail.com}{drupad.k.singh98@gmail.com} $\cdot$ +918085542513 $\cdot$ Hyderabad, IN \\
\end{center}
\vspace*{1mm}
%==== Experience ====%
\header{Work Experience}
\textbf{Software Engineer  \hfill United Health Group} \hfill July 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\small{\item As a serviceNow developer, created Cloning Automation tool which will automate the process of cloning one environment into another without losing critical data and functionality. It will be used by the organization for cloning Prod onto Dev as it will save around 130 hours of developer's work.}
\end{itemize}
\vspace{0mm}

\textbf{Backend Developer Intern  \hfill Brainyfied} \hfill May 2018 | Jun 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\small{\item Worked as a Backend Developer and created REST API using NodeJS+ ExpressJS and MYSQL(both relational and document based) Database for BrainyFied blog. It include JWT based Authentication system and Oauth for social account, APIs for Q&A section of the blog and profile.
	}
\end{itemize}
\vspace{0mm}

%==== Projects ====%
\header{Projects \hfill \sl \small{Portfolio: \href{http://orton009.github.io}{orton009.github.io}} \hfill \faGithub \sl \small{ \href{https://github.com/orton009}{github.com/orton009}}}

\textbf{Student Portal
\href{https://github.com/orton009}{\faGithub}}
\vspace{-1mm}
\begin{itemize}
	\small{\item Created a Web Platform where interested recruiters coming for on campus placements can shortlist candidates on the basis of their skills, projects and achievements. It can also be used by Department heads to select students according to their requirements for college projects.  }
	\small{\item Technology Stack -> NodeJS + ExpressJS , Angular2 , MongoDB  }
	\vspace{-1mm}
\end{itemize}

\textbf{Object Tracking System
\href{https://github.com/orton009}{\faGithub}}
\vspace{-1mm}
\begin{itemize}
	\small{\item Designed a surveillance system which can track a targeted pedestrian in multiple video inputs from cctv footage. It can differentiate between people on the basis of their unique features and can keep track of a particular person across different footage.}
	\small{\item Technology Stack -> OpenCV, python }
	\vspace{-1mm}
\end{itemize}

\textbf{Blog-starter-package
\href{https://github.com/orton009}{\faGithub}}
\vspace{-1mm}
\begin{itemize}
	\small{\item A boilerplate for NodeJS web Applications built using Node+Express, React and MySQL.}
	\small{\item It has local authentication using email and password, OAuth2.0 via Google and Facebook. MVC project structure, forgot and reset password links, Flash notifications, Account Management and some profile related APIs. }
	\small{\item It is generic and reusable on any new project from scratch or in any hackathon. APIs are well documented and it can be used in mobile Applications as well.}
\end{itemize}

\textbf{Online Food Ordering System
\href{https://github.com/orton009}{\faGithub}}
\vspace{-1mm}
\begin{itemize}
	\small{\item Created a web application which provides interface to select products online, add them to cart and send the order to the Restaurant. }
	\small{\item Technology Stack ->JSP , MYSQL , HTML5+CSS3+Bootstrap}
	\vspace{-1mm}
\end{itemize}

%==== Education ====%
\header{Education}
\vspace{2mm}
\textbf{Shri G.S. Institute of Technology and Science (Grade : 7.1)}\hfill Indore, IN\\
Bachelor of Engineering in Computer Science and Engineering \hfill Grad: Jun 2019\\
\vspace{2mm}
\textbf{Christ Jyoti Senior Secondary School (Percentage : 94.8)}\hfill Satna, IN\\
High School (physics, chemistry and Mathematics) \hfill Grad: May 2015\\
% Courses: Data Structures, Operating Systems, Algorithms, Computer Networks\\
%==== Skills ====%
\vspace*{2mm}
\header{Skills}
\begin{tabular}{ l l }
    \small{\textbf{Operating System}      & \small{Windows, Linux}      \\
	\small{\textbf{Languages}}      & \small{Javascript, C, SQL ,MongoDB , JAVA}      \\
	\small{\textbf{Libraries/Frameworks}} 
	&
	 \small{Angular, NodeJS, ExpressJS, GIT, BootStrap, REST, MEAN Stack}
	 \\
	\small{\textbf{Others}}                     &
	 \small{Data Structures , Algorithms, ServiceNow Platform}
	 \\
	 \small{\textbf{Interest}}                     &
	  Full Stack Web Development
\end{tabular}

%=== Online Courses ===%
\vspace{2mm}
\header{Online Courses}
\textbf{Angular 6 formerly Angular 2 from Udemy}\hfill\\
\vspace{2mm}
\textbf{The Complete NodeJS Developer (Basics to Advanced) from Udemy}\hfill \\
\vspace{2mm}
\textbf{Javascript ES6 from codeschool}\hfill \\
\vspace{2mm}

\end{document}